\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\section{Demo Plans}
 
We will be demonstrating all the core functionality that was specified in the requirements document and that was requested by our 
two supervisors. This includes:\\
\begin{itemize}
    \item Being able to login/register an account as a clinician or as a regular patient
    \item Being able to input and save multiple "patient profiles". These patient profiles will be the backbone of a trial search, and 
    contains things like medical condition, age, address, etc..
    \item Being able to search for clinical trials which are based on a previously entered "patient profile"
    \item Being able to save clincial trials that you are interested in
    \item Being able to view, edit, and delete your patient profiles
    \item Being able to view/delete your saved trials
\end{itemize}

\section{Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
David Moroniti & 8\\
Deep Raj & 8\\
Alan Scott 3 & 8\\
Anika Peer & 8\\
Aamina Hussain & 8\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
David Moroniti & 0\\
Deep Raj & 1\\
Alan Scott & 2\\
Anika Peer & 0\\
Aamina Hussain & 1\\
\bottomrule
\end{tabular}
\end{table}

As a result of us meeting regularly, and also talking in our teams chat on an almost daily basis, we don't feel it is necessary for 
everyone to attend every lecture. Generally, as long as one person is there, we feel as though we should be fine, as long as 
the person who goes is ok with (potentially) being the only one there.

\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 29 & 100\% \\
David Moroniti & 8 & 27.5\% \\
Deep Raj & 4 & 13.7\% \\
Alan Scott & 6 & 20.6\% \\
Anika Peer & 5 & 17.2\% \\
Aamina Hussain & 6 & 20.6\% \\
\bottomrule
\end{tabular}
\end{table}

Unfortunately, these numbers are not overly useful, since we work on feature branches, and squash/merge the branches into main
when we are done implementing the feature (we then delete the branch).

\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
David Moroniti & 25 & 10 \\
Deep Raj & 23 & 5 \\
Alan Scott & 15 & 7 \\
Anika Peer & 3 & 7 \\
Aamina Hussain & 1 & 6 \\
\bottomrule
\end{tabular}
\end{table}

David makes most of the issues for development work (while everyone is in the meeting, all watching the shared screen) and Deep makes
most of the issues for the team meetings/lectures. We want to mention that everyone contributes to the meetings (as seen in the meeting 
attendance table) and everyone contributes to the creation of the issues (i.e., what dev issues should be made, what should go in the 
description, etc..).

\section{CICD}

Currently, CICD is used lightly. We are currently just running some linters each time a PR is opened into main. After the code is checked
for proper formatting (i.e., passes linting) the next step in the pipeline runs the unit tests, to ensure tests are passing before merging
any new code. Any PR cannot be merged to main unless these 2 safety checks are met (note: as I am writing this, tests are not currently implemented,
so the testing portion of the pipeline does nothing. However, as tests are being added, it will become useful). We would like to add another 
pipeline which will be used to deploy our code to GCP after merging our code to the master branch. However, we are prioritizing the development
of the app for revision 0 for now, and will most likely not have this feature until after the revision 0 demo.

\end{document}